Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-20 main.tex
Updates from Overleaf

@@

The dynamics of the real system are described in continuous time. However, all the sensing and control performed on-board happen in discrete time, with time-step $\tau$. For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(n\tau)$.

@@

The objective of this section, as illustrated in \autoref{fig:interval-hull} is to  derive a \emph{set predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and a confidence region $\cC_\delta$ in the form \eqref{eq:generic-polytope} containing $A(\theta)$; and verifies the inclusion property:
\begin{equation}
\label{eq:interval_property}
\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq N\tau.
\end{equation}

@@

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(N\tau)=\overline{x}(N\tau)={x}(N\tau)\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}.

% Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
% \begin{gather*}
% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
% \end{gather*}
% where{\footnotesize{}
% \begin{gather*}
% \Upsilon=\left[\begin{array}{cccc}
% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
% P & Z_{+} & Z_{-} & -\Gamma
% \end{array}\right],\\
% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
% \mathcal{A}=\left[\begin{array}{cc}
% A_{0} & 0\\
% 0 & A_{0}
% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
% 0 & -\Delta A_{-}\\
% 0 & \Delta A_{+}
% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
% \Delta A_{+} & 0\\
% -\Delta A_{-} & 0
% \end{array}\right],
% \end{gather*}
% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

% \begin{example*}
% Consider a scalar system:
% \[
% \dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
% \]
% where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$. The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval_predictor}.

% \begin{figure}
% \begin{centering}
% \includegraphics[width=\linewidth]{img/interval_predictor}
% \par\end{centering}
% \caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue. The result of prediction by \eqref{eq:interval_predictor} is in red: the predictor is stable and produces tight bounds.}
% \label{fig:predictor_example}
% \end{figure}
% \end{example*}

@@

\begin{align}
\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards} \\
\hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu) \label{eq:surrogate_objective}
\end{align}
where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ does not respect the Markov assumption.

@@

The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g. a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.

In order to optimize our surrogate objective $\hat{V}^r$, we turn to sequential planning algorithms. We cannot use the Dynamic Programming techniques because the state space is continuous and the pessimistic rewards are non-markovian. Instead, we turn to tree-based planning algorithms which optimize a sequence of actions based on the corresponding sequence of rewards without enumerating the states nor requiring the markovity of the rewards. In particular, we use the \texttt{OPD} algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions, which is appropriate since both the predictor dynamics \eqref{eq:interval_predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.

\texttt{OPD} progressively builds a tree $\cT_k$ by expanding the leaf $a_k\in\cL_k$ with highest B-value:
\begin{equation}
\argmax_{a\in\cL_k} B_a(k), \quad B_a(k) = \sum_{n=0}^{h-1} \underline{R}_n(a) + \frac{\gamma^h}{A-\gamma}.
\end{equation}

\begin{proposition}
\label{prop:control-error}
If we assume that the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
\begin{equation*}
     V^r(\bu) - \hat{V}^r(\bu) = \cO\left(\frac{1}{\sqrt{N}}\right)
\end{equation*}
\end{proposition}

\begin{algorithm}[tb]
   \caption{Robust Estimation, Prediction and Control}
   \label{alg:full}
\begin{algorithmic}
   \STATE {\bfseries Input:} confidence level $\delta$
   \FOR{$N = 1,2,3,\dots$} 
   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
   \FOR{planning steps $[T]$}
   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval_predictor} using $\cC_{[N],\delta}$.
   \ENDFOR
   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
   \ENDFOR

@@

We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models.

@@

We express the performance of the planning problem in terms of a measure of the proportion of near-optimal paths:
\[
\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: V(a)\geq V - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
\]

@@

\begin{proof}
We have that $A(\theta) \in \cC_{[N],\delta}$ with probability $1-\delta$. Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$. This gives the following bound:
\begin{equation*}
 \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
\end{equation*}

And finally, with probability $1-\delta$,
\begin{align*}
v^r(\bu) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
\end{align*}
\end{proof}

@@

\begin{proof}
	For any $\theta \in \Theta$, $t \in [0, H]$ and any trajectory $(s_0, \cdots, s_t)$ sampled from $\pi$ and $T_\theta$,

	\begin{equation*}
	s_t \in S(t, s_0, \pi) \subset \square S(t, s_0, \pi)
	\end{equation*}

	Hence, 
	\begin{equation*}
	R^{T_\theta}_\pi = \sum_{t=0}^\infty \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \min_{s\in \square S(t, s_0, \pi)} \gamma^t r(s, \pi(s)) = \hat{v^r}(\pi)
	\end{equation*}

	And finally,
	\begin{align*}
	v^r(\pi) = \min_{\theta\in\Theta} {v_\pi^{T_\theta}} = \min_{\theta\in\Theta} \expectedvalue(R^{T_\theta}_\pi) \geq \hat{v^r}(\pi)
	\end{align*}
\end{proof}

>>>>

    Optimistic exploration = information seeking and uncertainty reduction. Our objective: do not commit mistakes (do not explore uncertain regions). If some information is collected allowing to reduce uncertainty, use it to be more optimal, but do not actively seek it.

@@

The dynamics of the real system are described in continuous time. However, all the sensing and control performed on-board happen in discrete time, with time-step $\tau$. For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\tau$.

@@

The objective of this section, as illustrated in \autoref{fig:interval-hull} is to  derive a \emph{set predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and a confidence region $\cC_\delta$ in the form \eqref{eq:generic-polytope} containing $A(\theta)$; and verifies the inclusion property:
\begin{equation}
\label{eq:inclusion-property}
\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq t_N.
\end{equation}

@@

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval-predictor} \\
 &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:inclusion-property}.

% Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
% \begin{gather*}
% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
% \end{gather*}
% where{\footnotesize{}
% \begin{gather*}
% \Upsilon=\left[\begin{array}{cccc}
% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
% P & Z_{+} & Z_{-} & -\Gamma
% \end{array}\right],\\
% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
% \mathcal{A}=\left[\begin{array}{cc}
% A_{0} & 0\\
% 0 & A_{0}
% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
% 0 & -\Delta A_{-}\\
% 0 & \Delta A_{+}
% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
% \Delta A_{+} & 0\\
% -\Delta A_{-} & 0
% \end{array}\right],
% \end{gather*}
% }then the predictor \eqref{eq:interval-predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

% \begin{example*}
% Consider a scalar system:
% \[
% \dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
% \]
% where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$. The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval-predictor}.

% \begin{figure}
% \begin{centering}
% \includegraphics[width=\linewidth]{img/interval-predictor}
% \par\end{centering}
% \caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue. The result of prediction by \eqref{eq:interval-predictor} is in red: the predictor is stable and produces tight bounds.}
% \label{fig:predictor_example}
% \end{figure}
% \end{example*}

@@

\begin{align}
\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards} \\
\hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu) \label{eq:surrogate_objective}
\end{align}
where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval-predictor}.
\end{definition}

This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ is not \emph{markovian}.

@@

The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g. a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed so they will not happen either when the controls are executed on the true system.

\paragraph{Planning}
In order to optimise $\hat{V}^r$, we turn to sequential planning algorithms. We cannot use Dynamic Programming algorithms because the state space is continuous and the pessimistic rewards are non-markovian. Instead, we turn to tree-based planning algorithms which optimise a sequence of actions based on the corresponding sequence of rewards. These methods no dot require the enumeration of the states nor the markovity of the rewards. In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions. Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: both the predictor dynamics \eqref{eq:interval-predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.

At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by expanding the leaf $a_k$ with highest B-value, where the expansion of a leaf $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$:
\begin{equation}
\label{eq:opd}
a_k = \argmax_{a\in\cL_k} B_a(k), \quad B_a(k) = \sum_{n=0}^{h(a)-1} \underline{R}_n(a) + \frac{\gamma^{h(a)}}{1-\gamma}
\end{equation}
where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the sequence $a$.
\begin{theorem}[Planning performance, \citep{Hren2008}]
\label{theorem:opd-regret}
The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} after $K$ iterations is:
\begin{align*}
\text{if } \kappa>1,\quad& 
\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);\\
\text{if }\kappa=1,\quad&
\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(\gamma^{\frac{(1-\gamma)^\beta}{c}K}\right)
\end{align*}
where $\kappa$ is a problem-dependent measure of the proportion of near-optimal paths:
\[
\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
\]
\end{theorem}

Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate. However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.

However, under an additional smoothness assumption on $R$, we can bound this gap:
\begin{proposition}
\label{prop:control-error}
If the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
\begin{equation*}
     V^r(\bu) - \hat{V}^r(\bu) = \cO\left(\frac{1}{\sqrt{N}}\right)
\end{equation*}
\end{proposition}

\begin{algorithm}[tb]
   \caption{Robust Estimation, Prediction and Control}
   \label{alg:full}
\begin{algorithmic}
   \STATE {\bfseries Input:} confidence level $\delta$
   \FOR{$N = 1,2,3,\dots$} 
   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
   \FOR{planning steps $[T]$}
   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
   \ENDFOR
   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
   \ENDFOR

@@

We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models, which all correspond to different modelling assumptions.

@@

@@

\begin{proof}
	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}. Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.

	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bw}, \overline{\bw}]$, we also have for any sequence of controls $\bu$:
	\begin{align*}
	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bw} \leq \bw \leq \overline{\bw}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
	    &= \hat{V}^r(\bu)
	\end{align*}
\end{proof}

\subsection{Proof of \autoref{prop:control-error}}

\begin{proof}
 By the inclusion property \eqref{eq:inclusion-property}, for any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$.

 Thus, since we assume that $R$ is $L$-lipschitz,
 \begin{align}
     V^r(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|
 \end{align}

@@
